\documentclass{resume} % Use the custom resume.cls style

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Resume for Paul Meier (www.morepaul.com)
%
% LaTeX Template Version 2.0 (8/5/13)
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------


\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\name{Pablo Meier} % Your name
\address{New York, NY} % Your address
\address{www.morepaul.com} % Your secondary addess (optional)
\address{(240) 535--3882 \\ pablo.a.meier@gmail.com} % Your phone number and email

\begin{document}
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Education}
{\bf Brown University} \hfill {June 2010} \\ 
B.S. in Computer Science\\
B.A. in Music\smallskip \\
\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Experience}

\begin{rSubsection}{Looksee}{April 2014 - January 2015}{Software Engineer -- Sup}{Java, JavaScript}
\item Built 3 Android apps from the ground up for publishing and subscribing to live video.
\item Designed and implemented Sup's server in Node.js.
\item Wrote a basic analytics platform to trend user behavior over time based on a Mongo dataset.
\end{rSubsection}
%------------------------------------------------
\begin{rSubsection}{Google}{August 2012 -- August 2013}{Software Engineer II --- API Console}{Java}
\item Implemented Notifications system for the Google API Console.
\item Reduced latency for internal API calls through parallelization.
\end{rSubsection}
%------------------------------------------------
\begin{rSubsection}{Adobe Systems, Inc.}{July 2010 -- June 2012}{Software
    Engineer --- Flash Platform}{C++, ActionScript, Java}
\item Implemented iOS Multitasking and Android SoftKeyboardEvents for AIR.
\item Primary engineer for AIR SDK, steering specs and adding functionality.
\item Lead a large-scale refactor of CorePlayer to detangle a deep inheritance
    chain, multiplied by many products built on the Platform.
\item Worked with and adapted to various platforms (Windows, OS X, Linux, Android, iOS).
\end{rSubsection}
\end{rSection}

%----------------------------------------------------------------------------------------
%	PROJECTS SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Projects}
\noindent{}\textbf{\textit{All projects available at https://github.com/pablo-meier/}}

\begin{rSubsection}{ScrabbleCheat}{2010 -- 2012}{\textit{Your neighborhood friendly Scrabble Solver}}{Erlang, C, Ruby}
\item Program to solve word-construction games like Scrabble, Words With Friends, and Lexulous.
\item Uses a custom-defined, pure-binary representation of an obscure data structure.
\item Demonstrates interoperability with libraries (Apache Thrift), multiple
    cooperating languages and paradigms, and comprehensive unit testing.
\end{rSubsection}

\begin{rSubsection}{Ebooker}{2012 -- 2013}{\textit{Markov chain-based Twitter poetry}}{Go}
\item Server and client to post tweets to Twitter built from a user's tweets using Markov chains.
\item Implements a full OAuth1 client (no OAuth library used).
\end{rSubsection}
\end{rSection}

%%----------------------------------------------------------------------------------------
%%	TECHNICAL STRENGTHS SECTION
%%----------------------------------------------------------------------------------------
% \begin{rSection}{Skills}
% \begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
% Languages & Java, JavaScript, C++, Ruby, Go, Erlang, Racket\\
% Spoken Languages & English, Spanish
% \end{tabular}
% \end{rSection}
\end{document}
